oscar_figures

### 2021-03-18 oscar_figures.Rmd
add itc bar graph

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DESeq2)
library(here)
library(ggrepel)
```

@@

```{r message=FALSE, warning=FALSE}
library(patchwork)

exon_snp <- 556 
intron_snp <- 1106
intron_start <- 141 
intron_end <- 1429
acceptor1 <- 394
acceptor2 <- 444
donor <- 572
mg_l <- 1624 
cpoor_start <- 490
cpoor_end <- 1325
risk_colour <- "#00BFC4"
healthy_colour <- "#F8766D"
confidence_interval <- 0.75  # fracion, i.e. 0.75 = 75%.
peak_threshold <- 5 # how many times above the mean to be a "peak"
region_length <- 50

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("tidyverse", "DESeq2", "here", "ggrepel", "patchwork")
```

@@

```{r message=FALSE, warning=FALSE}
exon_snp <- 556 
intron_snp <- 1106
intron_start <- 141 
intron_end <- 1429
acceptor1 <- 394
acceptor2 <- 444
donor <- 572
mg_l <- 1624 
cpoor_start <- 490
cpoor_end <- 1325
risk_colour <- "#00BFC4"
healthy_colour <- "#F8766D"
confidence_interval <- 0.75  # fracion, i.e. 0.75 = 75%.
peak_threshold <- 5 # how many times above the mean to be a "peak"
region_length <- 50

@@

## Isothermal Titration Calorimetry

Read in values

```{r warning=FALSE, message=FALSE}
df <- read_csv(paste0(here(), 
                      "/data/itc/itc final values.csv")) %>%
    group_by(RNA) %>%
    mutate(sd =sd(kd)) %>%
    mutate(mean_kd = mean(kd))

ggplot(df, aes(x = RNA, y = kd)) +
    geom_bar(aes(x = RNA, y = mean_kd), stat="identity", position="dodge") +
    geom_point() +
    geom_errorbar(aes(x=RNA, ymin = mean_kd-sd, ymax = mean_kd+sd),
                  width = 0.3) +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("")

t.test(df$kd[which(df$RNA=="H")], df$kd[which(df$RNA=="R")])
```
